---
title: "Capstone Project"
output:
  html_document: default
  html_notebook: default
---

This is a data visualization and manipulation part of our capstone project. The data is from AMC company. 

#### Background of this project

*	AMC Theaters Data Set of Loyalty Members
*	Insider members (free program) who have not upgraded
*	Premier members (paid program) who were once Insider members and upgraded to the paid program
*	Program information:  https://www.amctheatres.com/amcstubs 
*	Does not include customers who paid to be Premier without first having an Insider membership
*	Analysis focused on identifying people who have, or would, upgrade to the paid program
*	Each paid membership is $15/year
*	A 1% increase in paid program membership would yield approximately $xxx,xxx in membership revenue, in addition to lift from more engaged members

### Loading the data into R notebook

```{r}
amcdata<-read.csv("C:/Users/jiena_000/Desktop/Capstone Project/AMCSampleData_InsiderPremier.csv", stringsAsFactors = F )
head(amcdata)

```

### Summary table of data

```{r}
summary(amcdata)

```

### Check the frequency table of "IsPremier"

```{r}
table(amcdata$ISPREMIER)
```

Apparently, the data is imbalanced. Therefore, when we build a machine learning model, we have to check the AUC and ROC curve to have a better evaluation of models. 


### Check the Gender code
```{r}
table(amcdata$GENDERCODE)
```
*	0 is female
*	1 is male
*	3 is Unknown

### Correlation map
* Since the whole dataset has 24 variables, it might be too big to plot into one map. I classify them into four categories: biograph, notification, AMC stubs financial activities, Financial status and other AMC activities.

#### Correlation map of biograpic variables
Please note that I remove the gender is unknown data points. 
```{r}
library(corrplot)
 corrplot(cor(amcdata[,c(1:5)][which(amcdata$GENDERCODE!=3),]), method="number")

```

Obviously, "IsPremier" is not strongly related to any of biographic variables in this study. 

### Notification variables
The notification variables include:
* AMCSTUBSLOYALTYEMAILOFFEROPTININDICATOR - 0 is false; 1 is true
 *	Opted in to receive AMC Loyalty program email offers.
*	AMCSTUBSREWARDSEMAILOPTININDICATOR - 0 is false; 1 is true 
 *	Opted in to receive AMC Stubs emails.
*	AMCSTUBSREWARDSMOBILEOPTININDICATOR - 0 is false; 1 is true
 *  Opted in to receive AMC Stubs mobile notifications.
*	AMCSTUBSREWARDSSMSOPTININDICATOR - 0 is false; 1 is true
 *	Opted in to receive AM Stubs SMS messages.
*	AMCSTUBSTHEATREMOBILEOFFEROPTININDICATOR - 0 is false; 1 is true
 *	Opted in to receive AMC Stubs mobile theatre-level mobile offers.
*	AMCSTUBSTHEATRESMSOFFEROPTININDICATOR - 0 is false; 1 is true 
 *	Opted in to receive AMC Stubs theatre-level SMS offers.

```{r}
library(corrplot)
 corrplot(cor(amcdata[,c(1,7,8,9,10,11,12)]), method="number",tl.cex = 0.4 )

```
Apparently, "IsPremier" is not strongly related to any notification variables. 

### AMC stubs Member Financial Activities:
*	LIFETIMEAMCSTUBSAWARDSEARNEDAMOUNT
 *	Amount of rewards in dollars that an AMC Stubs member has earned.
*	LIFETIMEAMCSTUBSSPENDAMOUNT
 *	Amount of total spend by an AMC Stubs member.
*	ONLINEFEESWAIVEDAMOUNT
 *	Amount of dollars in online ticketing fees waived as an AMC Stubs member.
 
 
```{r}
library(corrplot)
 corrplot(cor(amcdata[,c(1,13,14,15)]), method="number",tl.cex = 0.4 )

```

If we consider the variables with correlation value about .2, then the "LIFETIMEAMCSTUBSAWARDSEARNEDAMOUNT" and "LIFETIMEAMCSTUBSSPENDAMOUNT" might be considered into modeling process. 

### Financial Status and other AMC activities

*	ESTIMATEDINCOMERANGE
 *	Axciom estimate of estimated income range for AMC Stubs member.
*	ESTIMATEDHOMEMARKETVALUERANGE
 *	Axcion estimated home market value range for AMC Stubs member.
*	CHILDRENPRESENCE - 0 is false; 1 is true
 *	Has children present in household.
*	HASFREQUENTVISITTHEATRENUMBER - 0 is false; 1 is true
 *	Has a most frequently visited theatre selected through the site or by another means.
*	TICKETQTYSUM	
 *	Number of tickets sold to this AMC Stubs member.
*	TICKETBALANCEDUESUM
 *	Total US dollar value of tickets sold to this AMC Stubs member.
*	CONCQTYSUM
 *	Total number of concession items purchased by this AMC Stubs member.
*	CONCLOYDISCOUNTAMTSUM
 *	Total amount of loyalty discount received by this AMC Stubs member (value in USD).
*	CONCBALANCEDUESUM
 *	Total US dollar value of concessions sold to this AMC Stubs member.

```{r}
library(corrplot)
 corrplot(cor(amcdata[,c(1,16,17,18,19,20,21,22,23,24)]), method="number",tl.cex = 0.4 )

```

From this result, we can see that "Is Premier" is strongly related (0.2 above) to "TICKETQTYSUM", "TICKETBALANCEDUESUM", "CONCQTYSUM", "CONCLOYDISCOUNTAMTSUM" and "CONCBALANCEDUESUM". 

### Correlation test for "Is Premier" with strong variables

```{r}
panel.cor <- function(x, y, digits=2, cex.cor)
{
  usr <- par("usr"); on.exit(par(usr))
  par(usr = c(0, 1, 0, 1))
  r <- abs(cor(x, y))
  txt <- format(c(r, 0.123456789), digits=digits)[1]
  test <- cor.test(x,y)
  Signif <- ifelse(round(test$p.value,3)<0.001,"p<0.001",paste("p=",round(test$p.value,3)))  
  text(0.5, 0.25, paste("r=",txt))
  text(.5, .75, Signif)
}

panel.smooth<-function (x, y, col = "blue", bg = NA, pch = 18, 
                        cex = 0.8, col.smooth = "red", span = 2/3, iter = 3, ...) 
{
  points(x, y, pch = pch, col = col, bg = bg, cex = cex)
  ok <- is.finite(x) & is.finite(y)
  if (any(ok)) 
    lines(stats::lowess(x[ok], y[ok], f = span, iter = iter), 
          col = col.smooth, ...)
}

panel.hist <- function(x, ...)
{
  usr <- par("usr"); on.exit(par(usr))
  par(usr = c(usr[1:2], 0, 1.5) )
  h <- hist(x, plot = FALSE)
  breaks <- h$breaks; nB <- length(breaks)
  y <- h$counts; y <- y/max(y)
  rect(breaks[-nB], 0, breaks[-1], y, col="cyan", ...)
}

pairs(amcdata[,c(1,13,14,20,21,22,23,24)],
      lower.panel=panel.smooth, upper.panel=panel.cor,diag.panel=panel.hist)


```

From the p-value of this graph, we can see that "Is Premier" is significantly correlated with "LIFETIMEAMCSTUBSAWARDSEARNEDAMOUNT", "LIFETIMEAMCSTUBSSPENDAMOUNT", "TICKETQTYSUM", "TICKETBALANCEDUESUM", "CONCQTYSUM", "CONCLOYDISCOUNTAMTSUM" and "CONCBALANCEDUESUM". I will use these seven variables to predict the "Is Premier". 



